Textual Features

### 2017-08-04 Hours.Rmd
made changes to summary_stats, continued fitting the model, tried to apply MLE and parametric distributions to the data

8/2/2017 | 5 | 1:15-6:15PM | Fitted CR models, changes summary_stats files..

>>>>

8/2/2017 | 5 | 1:15-6:15PM | Fitted CR models, changed summary_stats files
8/3/2017 | 5.5 | 12:00-5:30 | Added to summary stats, created ratio of newlines to textlength variable, tried to estimate MLEs, ran in to problems
8/3/2017 | 2.75 | 8:00-10:45 | Continued to try out MLEs, looked into Tex and downloaded mendeley, continued fitting the model

### 2017-08-04 model_fitting.Rmd
made changes to summary_stats, continued fitting the model, tried to apply MLE and parametric distributions to the data

#function to calculate r-square adjusted
get_r2adj <- function(cr_obj)
```

@@

#length of sentence till first punctuation mark 
x$first_punct <- str_locate(x$text, pattern = "[.|?|!]")[,1]

#if text contains punct
x$contain_punct <- FALSE
x$contain_punct[!is.na(x$first_punct)] <- TRUE

#if the text ends in a punctuation
x$end_punct <- str_detect(x$text, pattern = "[.|?|!]$")

#if the title ends in a question mark
x$contain_question <- str_detect(x$title, pattern = QUESTION %R% END)

#leaving out if title begins with "wh" (should i check if text is significant tho)
#if first letter of title is capitalized
x$capital_title <- str_detect(x$title, pattern = "^[[:upper:]]")

@@

x$all_lower <- str_detect(x$removed, pattern = "^[[:lower:]]+$")
x <- x[,-which(names(x) == "removed")]

@@

#average tag length
x$avg_tag_length <- NA
not_na <- which(x$tags != "")
for (i in not_na) {
  total_char <- sum(str_length(as.vector(split_tags[i,])))
  total_tags <- sum(as.vector(split_tags[i,]) != "")
  x$avg_tag_length[i] <- total_char / total_tags
}

@@

tag_freq <- tag_freq %>%
              arrange(desc(percent))

@@

x$avg_score <- (x$score1 + x$score2 + x$score3 + x$score4)/x$n_tags
x$avg_score[is.nan(x$avg_score)] <- 0

percentile80 <- quantile(x$avg_score, probs = 0.80)

x$frequent_tag <- FALSE
x$frequent_tag[x$avg_score >= percentile80] <- TRUE

@@

terms_a <- freq_terms(answered$title)
terms_a$prop_in_answered <- terms_a$frequency/nrow(terms_a)
colnames(terms_a)[2] <- "frequency_a"

@@

x$contain_u <- str_detect(as.character(x$title), pattern = or1(freq_terms_u$word))
x$contain_a <- str_detect(as.character(x$title), pattern = or1(freq_terms_a$word))

@@

```{r, echo = FALSE}
cr1 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + as.factor(pic_included) + 
               text_length + title_length + device_length + as.factor(new_user) + post_weekday + 
               as.factor(post_hour) + category + as.factor(categorized) + first_punct + 
               contain_punct + end_punct + contain_question + capital_text + all_lower + prior_effort + 
               gratitude + greeting + update + avg_tag_length + max_tagwords + avg_score + frequent_tag + 
               contain_toptag + contain_u + contain_a, data = x)
summary(cr1)
get_aic(cr1 , num_parameters = 70, data = x) #31604.12
```

```{r, echo = FALSE}
#removed categorized, contain_punct, end_punct, capital_text, max_tagwords
cr2 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + as.factor(pic_included) + 
               text_length + title_length + device_length + as.factor(new_user) + post_weekday + 
               as.factor(post_hour) + category + first_punct + 
               contain_question + all_lower + prior_effort + 
               gratitude + greeting + update + avg_tag_length + avg_score + frequent_tag + 
               contain_toptag + contain_u + contain_a, data = x)
summary(cr2)
get_aic(cr2, 66, data = x) #31594.76
 70794.28
```

```{r, echo = FALSE}
#removed n_tags (-4) and added tag_included (+1), took out average_tag length (-1)
cr3 <- coxph(Surv(time_until_answer, answered)~as.factor(tag_included) + as.factor(pic_included) + 
               text_length + title_length + device_length + as.factor(new_user) + post_weekday + 
               as.factor(post_hour) + category + first_punct + 
               contain_question + all_lower + prior_effort + 
               gratitude + greeting + update + avg_score + frequent_tag + 
               contain_toptag + contain_u + contain_a, data = x)
summary(cr3)
get_aic(cr3, 61, data = x) #70794.28

#took out post_weekday (-6), added back in average tag length (+1), take out post_hour (-23)
cr4 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + as.factor(pic_included) + 
               text_length + title_length + device_length + as.factor(new_user) + 
               category + first_punct + 
               contain_question + all_lower + prior_effort + 
               gratitude + greeting + update + avg_tag_length + avg_score + frequent_tag + 
               contain_toptag + contain_u + contain_a, data = x)
summary(cr4)
get_aic(cr4, 37, data = x) #31594.91 cr2 = 31594.76

#remove title and text length (-2) 
cr5 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + as.factor(pic_included) + 
               device_length + as.factor(new_user) + 
               category + first_punct + 
               contain_question + all_lower + prior_effort + 
               gratitude + greeting + update + avg_tag_length + avg_score + frequent_tag + 
               contain_toptag + contain_u + contain_a, data = x)
summary(cr5)
get_aic(cr5, 35, data = x) #31591.15

#remove if pic included and gratitude 
cr6 <- coxph(Surv(time_until_answer, answered)~as.factor(n_tags) + 
               device_length + as.factor(new_user) + 
               category + first_punct + 
               contain_question + all_lower + prior_effort + 
               greeting + update + avg_tag_length + avg_score + frequent_tag + 
               contain_toptag + contain_u + contain_a, data = x)
summary(cr6)
get_aic(cr6, 33, data = x) #31589.07

cr7 <- coxph(Surv(time_until_answer, answered)~ device_length + as.factor(new_user) + 
               category + first_punct + 
               contain_question + all_lower + prior_effort + 
               greeting + update + avg_tag_length + avg_score + 
               contain_u + contain_a, data = x)
summary(cr7)
get_aic(cr7, 27, data = x) #31580.82

#remove prior effort
cr8 <- coxph(Surv(time_until_answer, answered)~ device_length + as.factor(new_user) + 
               category + first_punct + 
               contain_question + all_lower + 
               greeting + update + avg_tag_length + avg_score + 
               contain_u + contain_a, data = x)
summary(cr8)
get_aic(cr8, 26, data = x) #31581.15

#add prior effort back 
cr7 <- coxph(Surv(time_until_answer, answered)~ device_length + as.factor(new_user) + 
               category + first_punct + 
               contain_question + all_lower + prior_effort + 
               greeting + update + avg_score + 
               contain_u + contain_a, data = x)
summary(cr7)
get_aic(cr7, 27, data = x) #31,580.82 70,819.65

>>>>

#function to calculate r-square adjusted
get_rsq_adj <- function(cr_obj, k) {
  r <- unname(summary(cr_obj)$rsq[1])
  n <- summary(cr_obj)$n
  radj <- 1- (((1- (r**2)) * (n - 1))/(n-k-1))
  return(radj)
}

#function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n and stopwrds are an optional arguments
freq_terms <- function(vec, n = NULL, stopwrds = NULL) {
  source <- VectorSource(vec)
  corpus <- VCorpus(source)

  if (is.null(stopwrds)) {
    cleaned_corpus <- clean_corpus(corpus) 
    dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = weightTfIdf))
    m <- as.matrix(dtm) 
    freq <- colSums(m)
    freq <- sort(freq, decreasing = TRUE)
    freq_df <- data.frame(word = names(freq), frequency = unname(freq))    
  } else {
    cleaned_corpus <- clean_corpus(corpus, stopwrds) 
    dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = weightTfIdf))
    m <- as.matrix(dtm) 
    freq <- colSums(m)
    freq <- sort(freq, decreasing = TRUE)
    freq_df <- data.frame(word = names(freq), frequency = unname(freq))
  }

  if (missing(n)) {
    return(freq_df)
  }
  else {
    return(freq_df[1:n,])
  }
}
```

@@

#length of sentence till first punctuation mark 
x$text_till_punct <- str_locate(x$text, pattern = "[.|?|!]")[,1]
x$text_till_punct[is.na(x$text_till_punct)] <- 5000

#if text contains end punctuation
x$contain_punct <- FALSE
x$contain_punct[!is.na(x$text_till_punct)] <- TRUE

#if the text ends in a punctuation
x$text_end_punct <- str_detect(x$text, pattern = "[.|?|!]$")

#if the title ends in a question mark
x$title_questionmark <- str_detect(x$title, pattern = QUESTION %R% END)

#if the title starts with "Wh"
x$title_begin_wh <- str_detect(str_to_lower(x$title), pattern = "^wh")

#if first letter of title is capitalized
x$capital_title <- str_detect(x$title, pattern = "^[[:upper:]]")

@@

x$text_all_lower <- str_detect(x$removed, pattern = "^[[:lower:]]+$")
x <- x[,-which(names(x) == "removed")]

@@

#average tag length
x$avg_tag_length <- NA
not_na <- which(x$tags != "")
for (i in not_na) {
  total_char <- sum(str_length(as.vector(split_tags[i,])))
  total_tags <- sum(as.vector(split_tags[i,]) != "")
  x$avg_tag_length[i] <- total_char / total_tags
}
x$avg_tag_length[is.na(x$avg_tag_length)] <- 0

@@

tag_freq <- tag_freq %>%
              arrange(desc(percent))
top50 <- tag_freq[1:50,]

@@

x$avg_tag_score <- (x$score1 + x$score2 + x$score3 + x$score4)/x$n_tags
x$avg_tag_score[is.nan(x$avg_tag_score)] <- 0

percentile80 <- quantile(x$avg_tag_score, probs = 0.80)

x$frequent_tag <- FALSE
x$frequent_tag[x$avg_tag_score >= percentile80] <- TRUE

@@

library(qdap)
library(tm)
terms_a <- freq_terms(answered$title)
terms_a$prop_in_answered <- terms_a$frequency/nrow(terms_a)
colnames(terms_a)[2] <- "frequency_a"

@@

x$contain_unanswered <- str_detect(as.character(x$title), pattern = or1(freq_terms_u$word))
x$contain_answered <- str_detect(as.character(x$title), pattern = or1(freq_terms_a$word))

#ratio of newlines to length of text
x$newline_ratio <- str_count(x$text, pattern = "\n")/str_length(x$text)

@@

```{r, echo = FALSE}
cr1 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
                  text_end_punct + title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  greeting + update + avg_tag_length + max_tagwords + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
s <- summary(cr1)
s$rsq
get_aic(cr1, 72, data = x) #83471.68
get_rsq_adj(cr1, 72) #0.00513921

#removed greeting and text_end punct (p-values > .8)
cr2 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_length + max_tagwords + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr2)
get_aic(cr2, 70, data = x) #83467.71
get_rsq_adj(cr2, 70) #0.005397121

#removed max_tagwords
cr3 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_length + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr3)
get_aic(cr3, 69, data = x) #83465.91
get_rsq_adj(cr3, 69) #0.005520927

#removed avg_tag_length
cr4 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
                  device_length + post_weekday + as.factor(post_hour) + text_till_punct + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr4)
get_aic(cr4, 68, data = x) #83463.95
get_rsq_adj(cr4, 68) #0.005649183

#removed text_till_punct
cr5 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(n_tags) + as.factor(pic_included) + text_length + title_length + 
                  device_length + post_weekday + as.factor(post_hour) + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr5)
get_aic(cr5, 67, data = x) #83462.4
get_rsq_adj(cr5, 67) #0.005766099

#removing n_tags
cr6 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(pic_included) + text_length + title_length + 
                  device_length + post_weekday + as.factor(post_hour) + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr6)
get_aic(cr6, 63, data = x) # 83455.8
get_rsq_adj(cr6, 63) #0.00624444

#remove text_length
cr7 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(pic_included) + title_length + 
                  device_length + post_weekday + as.factor(post_hour) + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr7)
get_aic(cr7, 62, data = x) #83455.28
get_rsq_adj(cr7, 62) #0.006333204

#remove title_length
cr8 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  as.factor(pic_included) + 
                  device_length + post_weekday + as.factor(post_hour) + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr8)
get_aic(cr8, 61, data = x) #83454.54
get_rsq_adj(cr8, 61) #0.006427927

#remove pic_included
cr9 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  device_length + post_weekday + as.factor(post_hour) + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + prior_effort + gratitude + 
                  update + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr9)
get_aic(cr9, 60, data = x) #83454.3
get_rsq_adj(cr9, 60) #0.0065088

#remove prior_effort
cr10 <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + 
                  device_length + post_weekday + as.factor(post_hour) + 
                  title_questionmark + title_begin_wh + 
                  capital_title + capital_text + text_all_lower + gratitude + 
                  update + avg_tag_score + 
                  frequent_tag + contain_toptag + contain_unanswered + contain_answered + 
                  newline_ratio, data = x)
summary(cr10)
get_aic(cr10, 59, data = x) #83454.39 aic went up 
get_rsq_adj(cr10, 59) #0.00658092

### 2017-08-04 summary_stats.Rmd
made changes to summary_stats, continued fitting the model, tried to apply MLE and parametric distributions to the data

library(ggplot2)
library(survival)
library(epiR)
library(survminer)

proportion_answered <- sum(x$answered)/nrow(x)
```

@@

* `r nrow(x)` observations
* `r round(proportion_answered * 100, digits = 2)` % of questions were answered

@@

```{r, echo = FALSE}
summary <- summary(x$time_until_answer)
```

* **minimum:** `r round(min(x$time_until_answer), 2)` hrs
* **maximum:** `r round(max(x$time_until_answer), 2)` hrs (`r round(max(x$time_until_answer)/24, 2)` days)
* **mean:** `r round(mean(x$time_until_answer), 2)` hrs (`r round(mean(x$time_until_answer)/24, 2)` days)
* **median:** `r round(median(x$time_until_answer), 2)` hrs
* **first quartile:** `r round(summary[2], 2)`hrs
* **third quartile:** `r round(summary[5], 2)` hrs (`r round(summary[5]/24, 2)` days)
* **IQR range:** `r round(summary[5] - summary[2], 2)` hrs (`r round((summary[5] - summary[2])/24, 2)` days)
* Within an hour, `r round((sum(x$time_until_answer <= 1)/nrow(x))*100,2)`% of the questions have been answered
* Within 5 hours, `r round((sum(x$time_until_answer <= 5)/nrow(x))*100,2)`% of the questions have been answered

@@

##### Based off of the Kaplan-Meier Estimator 
```{r, echo = FALSE}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")

@@

```{r, percentiles, echo = FALSE}
quant <- quantile(KM, c(0.01, 0.10, 0.25, 0.30, 0.50, 0.64, 0.75))
round(quant[[1]], 3)
```
* Interpretations:
    + By `r round(quant$quantile[1], 2)` hrs 1% of the questions have been answered
    + By `r round(quant$quantile[2], 2)` hrs 10% of the questions have been answered
    + By `r round(quant$quantile[3], 2)` hrs 25% of the questions have been answered
    + By `r round(quant$quantile[4], 2)` hrs 30% of the questions have been answered
    + By `r round(quant$quantile[5], 2)` hrs 50% of the questions have been answered
    + 75th percentile doesn't exist (lowest survival probability: `r round(min(summary(KM)$surv),2)`)
    + highest quantile that exists: By `r round(quant$quantile[6], 2)` hrs (`r round(quant$quantile[6]/24, 2)` days) 64% of the questions have been answered

##### Survival Curves

* Survival curve shows that survival probability drops immediately after question is posted. 
* Within a few hours after posting, the survival probability levels out (though it still decreases at a slow rate), and hovers around 0.35 (never hits 0).

```{r, survival curves, echo = FALSE}
ggsurvplot(KM, data = x, risk.table = TRUE, xlab = "Time (hours)", title = "KM Curve")
```

```{r, echo = FALSE}
ggsurvplot(KM, data = x, risk.table = FALSE, xlab = "Time (hours)", title = "KM Curve (zoomed in)", xlim = c(0,50), break.x.by = 10)
```

##### Reversing the survival curves

@@

```{r, echo = FALSE}
reversed <- data.frame(time = s$time, prob_ans = 1-s$surv)
ggplot(reversed, aes(x = time, y = prob_ans)) + 
  geom_line() + 
  scale_x_continuous("Time (hours)", limits = c(0,100)) + 
  scale_y_continuous("Probability a question is answered before time t") + 
  ggtitle("Probability a question is answered before a certain time vs. time (hours)")
```

##### Instantaneous Hazard Rates (based off of KM estimates)

```{r, instant hazard, echo = FALSE}
h.hat <- epi.insthaz(KM, conf.level = 0.95) #instantaneous hazard on basis of KM 
round(head(h.hat), 3)
```

* Max instant hazard rate: `r round(max(h.hat$est), 2)` at `r round(h.hat$time[which(h.hat$est == max(h.hat$est))], 2)` hrs 
* Min instant hazard rate: `r round(min(h.hat$est), 2)`
* Interpretations: 
    +

```{r, instant hazard plots, echo = FALSE}
ggplot(h.hat, aes(x = time, y = est)) + 
  geom_line() + 
  scale_x_continuous("Time (hours)") + 
  scale_y_continuous("Instantaneous Hazard Rate") + 
  ggtitle("Instantaneous Hazard Rate Plot")

ggplot(h.hat, aes(x = time, y = est)) + 
  geom_line() + 
  scale_x_continuous("Time (hours)", limits = c(0,50)) + 
  scale_y_continuous("Instantaneous Hazard Rate") + 
  ggtitle("Instantaneous Hazard Rate Plot (zoomed in)")
```

* Instant hazard rate of a question getting answered drops to 0 and stays there pretty consistently after about 45 hours
* Right before that 45th hour, hazard spikes up twice to about 1.25

##### Cumulative Hazard Rates

@@

```{r, echo = FALSE}
#KM estimator of cumulative hazard 
fit <- data.frame(surv = s$surv, time = s$time, n.event = s$n.event, n.risk = s$n.risk)
fit$H.hat <- -log(fit$surv)

ggplot(fit, aes(x = time, y = H.hat)) + 
  geom_line() + 
  scale_x_continuous("Time (hours)") + 
  scale_y_continuous("Cumulative Hazard Rate based off of KM Estimates") + 
  ggtitle("Cumulative Hazard Plot (KM)")

#Nelson-Aalen estimator of cumulative hazard
fit$H.tilde <- cumsum(fit$n.event/fit$n.risk)

ggplot(fit, aes(x = time, y = H.tilde)) +
  geom_line() +
  scale_x_continuous("Time (hours)", limits = c(0,1000)) +
  scale_y_continuous("Cumulative Hazard Rate based off of Nelson Aalen Type") + 
  ggtitle("Cumulative Hazard Plot (Nelson-Aalen)")
```

>>>>

library(ggplot2)
library(survival)
library(epiR)
library(survminer)
library(dplyr)
```

@@

* `r nrow(x)` observations
* `r ncol(x)` variables

@@

```{r, echo = FALSE}
summary <- summary(x$time_until_answer)
proportion_answered <- sum(x$answered)/nrow(x)
```

* **Shortest answer time:** `r round(min(x$time_until_answer), 2)` hrs
* **Longest answer time (not answered):** `r round(max(x$time_until_answer), 2)` hrs (`r round(max(x$time_until_answer)/24, 2)` days)
* **mean:** `r round(mean(x$time_until_answer), 2)` hrs (`r round(mean(x$time_until_answer)/24, 2)` days)
* **median:** `r round(median(x$time_until_answer), 2)` hrs
* **first quartile:** `r round(summary[2], 2)` hrs
* **third quartile:** `r round(summary[5], 2)` hrs (`r round(summary[5]/24, 2)` days)
* **IQR range:** `r round(summary[5] - summary[2], 2)` hrs (`r round((summary[5] - summary[2])/24, 2)` days)
* `r round(proportion_answered*100, digits = 2)`% of questions were answered (complete)
* Within an hour, `r round((sum(x$time_until_answer <= 1)/nrow(x))*100,2)`% of the questions have been answered
* Within 5 hours, `r round((sum(x$time_until_answer <= 5)/nrow(x))*100,2)`% of the questions have been answered

@@

##### Based off of the Kaplan-Meier Estimator 
```{r, include = FALSE}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")

@@

* Table of percentiles:

```{r, percentiles, echo = FALSE}
quant <- quantile(KM, c(0.01, 0.10, 0.25, 0.30, 0.50, 0.64, 0.75))
round(quant[[1]], 3)
```
* Interpretations:
    + By `r round(quant$quantile[1], 2)` hrs 1% of the questions have been answered
    + By `r round(quant$quantile[2], 2)` hrs 10% of the questions have been answered
    + By `r round(quant$quantile[3], 2)` hrs 25% of the questions have been answered
    + By `r round(quant$quantile[4], 2)` hrs 30% of the questions have been answered
    + By `r round(quant$quantile[5], 2)` hrs 50% of the questions have been answered
    + 75th percentile doesn't exist (lowest survival probability: `r round(min(summary(KM)$surv),2)`)
    + Highest quantile that exists: By `r round(quant$quantile[6], 2)` hrs (`r round(quant$quantile[6]/24, 2)` days) 64% of the questions have been answered

##### Kaplan-Meier Survival Curve

```{r, echo = FALSE}
ggsurvplot(KM, data = x, 
           risk.table = "abs_pct", risk.table.title = "Total number at risk (percentage at risk)",
           cumevents = TRUE, 
           censor = FALSE, 
           conf.int = TRUE, conf.int.style = "step", 
           surv.median.line = "hv", 
           xlab = "Time (hours)", 
           surv.plot.height = 1, ggtheme = theme_bw(),
           tables.height = 0.15, tables.theme = theme_cleantable(), fontsize = 3)
```

##### Kaplan-Meier Survival Curve showing up to 100 hours

```{r, echo = FALSE}
ggsurvplot(KM, data = x, 
           risk.table = "abs_pct", risk.table.title = "Total number at risk (percentage at risk)", 
           cumevents = TRUE, 
           conf.int = TRUE, conf.int.style = "step", 
           censor = FALSE,
           surv.median.line = "hv", 
           xlab = "Time (hours)", 
           xlim = c(0, 100), break.x.by = 10,
           ylim = c(0, 0.7), break.y.by = 0.1,
           surv.plot.height = 1, ggtheme = theme_bw(), 
           tables.height = 0.15, tables.theme = theme_cleantable(), fontsize = 2, na.rm = TRUE)
```

* KM survival curve shows that the probability a question survives (remains unanswered) past a certain time drops immediately after question is posted.
* Within ~ 100 hours after posting, the survival probability levels out (though it still decreases at a slow rate), and hovers around 0.35 (never hits 0).
* Dashed marks around the lines represent the point-wise 95% confidence intervals
* Vertical dashed line on the plots indicates the median survival time

##### Reversing the survival curve

@@

```{r, echo = FALSE}
reversed <- data.frame(time = s$time, prob_ans = 1-s$surv)
ggplot(reversed, aes(x = time, y = prob_ans)) + 
  geom_line(na.rm = TRUE) + 
  scale_x_continuous("Time (hours)", limits = c(0,100)) + 
  scale_y_continuous("Probability a question is answered before time t") + 
  ggtitle("Probability a question is answered before a certain time vs. time (hours)")
```

##### Kaplan-Meier Type Instantaneous Hazard

```{r, instant hazard, echo = FALSE}
h.hat <- epi.insthaz(KM, conf.level = 0.95) #instantaneous hazard on basis of KM 
round(h.hat[1:10,], 4)
```

* Max KM instant hazard rate: `r round(max(h.hat$est), 2)` at `r round(h.hat$time[which(h.hat$est == max(h.hat$est))], 2)` hrs 
* Min KM instant hazard rate: `r round(min(h.hat$est), 2)`
* Interpretations: 
    + h(t = 0.0083) = 0.0155: Questions that have not been answered 0.0083 (0.498 min) hours after posting, are estimated to be answered 0.015 times within the next 0.0006 hours (0.036 min). 
    + h(t = 0.0164) = 0.9289: Questions that have not been answered 0.0164 (0.984 min) hours after posting, are estimated to be answered 0.9289 times within the next 0.0008 hours (0.048 min).

```{r, instant hazard plots, echo = FALSE}
ggplot(h.hat, aes(x = time, y = est)) + 
  geom_line() + 
  scale_x_continuous("Time (hours)") + 
  scale_y_continuous("Instantaneous Hazard") + 
  ggtitle("KM Type Instantaneous Hazard Plot")

ggplot(h.hat, aes(x = time, y = est)) + 
  geom_line(na.rm = TRUE) + 
  scale_x_continuous("Time (hours)", limits = c(0,500), breaks = seq(0, 500, by = 50)) + 
  scale_y_continuous("Instantaneous Hazard") + 
  ggtitle("KM Type Instantaneous Hazard Plot showing up to 500 hours")
```

* After about 150 hours, the KM instant hazard of a question getting answered drops to 0 and stays there pretty consistently, with a few small spikes here and there
* Right before that 45th hour, hazard spikes up twice to about 1.25

##### Nelson-Aalen Type Instantaneous Hazard Rate

```{r, echo = FALSE}
fit <- data.frame(surv = s$surv, time = s$time, n.event = s$n.event, n.risk = s$n.risk)
fit$h.tilde <- fit$n.event/fit$n.risk

a <- fit %>%
  select(time = time, estimate = h.tilde, num_experience_event = n.event, num_at_risk = n.risk)
a[1:10,]
```

* Max Nelson-Aalen Type Hazard: `r round(max(fit$h.tilde, na.rm = TRUE),5)` at `r round(fit$time[which(fit$h.tilde == max(fit$h.tilde, na.rm = TRUE))],2)` hours
* Min Nelson-Aalen Type Hazard: `r min(fit$h.tilde, na.rm = TRUE)` at `r round(fit$time[which(fit$h.tilde == min(fit$h.tilde, na.rm = TRUE))],2)` hours
* Interpretations:
    + h(t = 0.0083) = 0.000129: Given that a randomly selected question has not been answered by 0.0083 hours (0.498 min), the estimated probability that a question is answered in the next 0.0006 hours is 0.000129.
    + h(t = 0.0164) = 0.000258: Given that a randomly selected question has not been answered by 0.0164 hours (0.984 min), the estiamted probability that a question is answered in the next 0.0008 hours is 0.000258.

```{r, echo = FALSE}
ggplot(fit, aes(x = time, y = h.tilde)) + 
  geom_line() + 
  scale_x_continuous("Time (hours)") + 
  scale_y_continuous("Instantaneous Hazard") + 
  ggtitle("Nelson-Aalen Type Instantaneous Hazard Plot")

ggplot(fit, aes(x = time, y = h.tilde)) + 
  geom_line(na.rm = TRUE) + 
  scale_x_continuous("Time (hours)", limits = c(0,25)) + 
  scale_y_continuous("Instantaneous Hazard") + 
  ggtitle("Nelson-Aalen Type Instantaneous Hazard Plot, showing up to 25 hours")
```

##### Cumulative Hazard

@@

```{r, echo = FALSE}
#Nelson-Aalen estimator of cumulative hazard
fit$H.tilde <- cumsum(fit$h.tilde)

ggplot(fit, aes(x = time, y = H.tilde)) +
  geom_line(na.rm = TRUE) +
  scale_x_continuous("Time (hours)", limits = c(0,1000), breaks = seq(0, 1000, by = 100)) +
  scale_y_continuous("Cumulative Hazard Rate based off of Nelson Aalen Type") + 
  ggtitle("Cumulative Hazard Plot (Nelson-Aalen)")

#KM estimator of cumulative hazard 
fit$H.hat <- -log(fit$surv)

ggplot(fit, aes(x = time, y = H.hat)) + 
  geom_line() + 
  scale_x_continuous("Time (hours)") + 
  scale_y_continuous("Cumulative Hazard Rate based off of KM Estimates") + 
  ggtitle("Cumulative Hazard Plot (KM)")
```

### 2017-08-04 textual_analysis.Rmd
made changes to summary_stats, continued fitting the model, tried to apply MLE and parametric distributions to the data

>>>>

### Ratio of newlines to text length

```{r, echo = FALSE}
x$newline_ratio <- str_count(x$text, pattern = "\n")/str_length(x$text)
prop_newline <- sum(x$newline_ratio != 0)/nrow(x)
```

* `r round(prop_newline*100,2)`% of questions contain any newlines 
* largest ratio: `r max(x$newline_ratio)`
* smallest ratio: `r min(x$newline_ratio)`
* median ratio: `r median(x$newline_ratio)`
* mean ratio: `r mean(x$newline_ratio)`

```{r, echo = FALSE}
ggplot(x, aes(x = newline_ratio)) + 
  geom_histogram(bins = 30) + 
  ggtitle("Distribution of newline_ratios")
```

##### median newline_ratio grouped by answered/unanswered

```{r, echo = FALSE}
x %>%
  group_by(answered) %>%
  summarise(mean_ratio = mean(newline_ratio), median_ratio = median(newline_ratio))
```
